\setlength\parindent{0cm}
{\LARGE Lyle M. Gordon}\\[0.5cm]

\noindent\begin{minipage}[t]{0.6\textwidth}
Department of Materials Science and Engineering\\
Northwestern University\\
2220 Campus Drive\\
Evanston, IL. 60208\\
USA
\end{minipage}%
\hfill
\begin{minipage}[t]{0.4\textwidth}
\Telefon \ {\small{office}}: 847-491-3584\\
%\phantom{\Telefon \ }{\small{home}}: 858-777-8782\\
%\phantom{\Telefon \ }{\small{cell}}: 847-400-4071\\
\Letter: \href{mailto:lyle@lylegordon.ca}{lyle@lylegordon.ca}\\
\textsc{url}: \href{http://lylegordon.ca}{http://lylegordon.ca}
\end{minipage}\\[2.5mm]

%\textbf{Citizenship}: Canadian

\section*{\large{Areas of Specialization}}
Atom probe tomography • Organic-inorganic interfaces • Biomineralization

\section*{Education}
\years{2008-}\textbf{PhD Candidate in Materials Science and Engineering}\\*
\begingroup\setlength{\parskip}{0.2cm}
\emph{Northwestern University}. Evanston, IL. Expected 2013\\*
\textsc{thesis} : Buried Organic-Inorganic Interfaces in Biological Minerals\\*
\textsc{advisor} : Dr. Derk Joester

\years{2008}\textbf{BASc with Honours in Materials Science and Engineering}\\*
\emph{University of Toronto}, Toronto, ON.
\endgroup

\section*{Research Experience}
\years{2008-}\textbf{Biomineral Engineering Group}, Materials Science and Engineering, Northwestern University.\\*
\begingroup\setlength{\parskip}{0.2cm}
\textsc{advisor} : Dr. Derk Joester\\*
Characterization of nanoscale buried organic-inorganic interfaces in biological minerals with atom-probe tomography.

\years{2007-2008}\textbf{Hybrid Materials Group}, Materials Science and Engineering, University of Toronto.\\*
\textsc{advisor} : Dr. Glenn D. Hibbard\\*
Developed and characterized a sub-millimetre scale periodic cellular material fabricated using rapidprototyping and electrodeposition of high-strength nanocrystalline nickel.

\years{2004-2008}\textbf{Concrete Canoe Team}, Civil Engineering, University of Toronto.\\*
\textsc{advisor} : Dr. Kim D. Pressnail\\*
Coordinated the development, testing and implementation of a carbon fiber reinforced polymer modified lightweight aggregate concrete composite for use in the construction of a racing canoe.

\years{2007}\textbf{Orthopaedic Biomechanics Lab}, Sunnybrook Health Sciences Centre.\\*
\textsc{advisor} : Dr. Cari M. Whyne.\\*
Characterized the mechanical and biological properties of a elastin-hyaluronan composite hydrogel for tissue engineering of the nucleus pulposus.

\years{2006}\textbf{Orthopaedic Biomechanics Lab}, Sunnybrook Health Sciences Centre.\\*
\textsc{advisor} : Dr. Cari M. Whyne.\\*
Developed and validated a finite element model of pelvic lateral compression fracture stability.

\years{2005}\textbf{Orthopaedic Biomechanics Lab}, Sunnybrook Health Sciences Centre.\\*
\textsc{advisor} : Dr. Cari M. Whyne.\\*
Developed a 3D atlas-based method to automate segmentation of metastatic vertebrae on X-ray computed tomography scans.
\endgroup

\section*{Professional Experience}
\years{2012}\textbf{PreScouter}, Evanston, IL.\\*
\begingroup\setlength{\parskip}{0.2cm}
\textsc{Technology Consultant}\\
Technology scouter connecting coorporate innovators to new technologies.  

\section*{Teaching}
\years{2012}\textbf{Biominerals: Hierarchical Architecture and Function}, Northwestern University.\\*
\begingroup\setlength{\parskip}{0.1cm}
Lecture on the structure and function of the chiton tooth.

\years{2011}\textbf{Introduction to Materials Science}, Northwestern University.\\*
Laboratory assistant.

\years{2009}\textbf{Introduction to Materials Science}, Northwestern University.\\*
Teaching and laboratory assistant.

\years{2009}\textbf{Introduction to Materials Science}, Northwestern University.\\*
Teaching and laboratory assistant.
\endgroup

\section*{Grants, Honours \& Fellowships}
\years{2012-2013}\textbf{Terminal Year Fellowship}. McCormick School of Engineering, Northwestern University.

\begingroup\setlength{\parskip}{0.1cm}
\years{2010-2012}\textbf{Postgraduate Scholarship, Doctorate}. National Science and Engineering Research Council of Canada.

\years{2009-2010}\textbf{Postgraduate Scholarship Extension, Masters}. National Science and Engineering Research Council of Canada.

\years{2008-2009}\textbf{Appointed University Scholar}. The Graduate School, Northwestern University.

\years{2008}\textbf{Walter P. Murphy Fellowship}. Department of Materials Science and Engineering, Northwestern University.

\years{2008-2009}\textbf{Postgraduate Scholarship, Masters}. National Science and Engineering Research Council of Canada.

\years{2008}\textbf{Alexander Graham Bell Canada Graduate Scholarship, Masters}. National Science and Engineering Research Council of Canada, \emph{declined}.

\years{2008}\textbf{Ontario Graduate Scholarship, Masters}. Ontario Graduate Scholarship Program, \emph{declined}.

\years{2008}\textbf{Stanford Graduate Fellowship}. Stanford University, \emph{declined}.

\years{2004-2008}\textbf{Dean's Honour List}. Faculty of Applied Science and Engineering, University of Toronto. \emph{(4 years)}

\years{2007-2008}\textbf{Stelco Scholarship}. Department of Materials Science and Engineering, University of Toronto.

\years{2007}\textbf{Undergraduate Student Research Award}. National Science and Engineering Research Council of Canada. 

\years{2005-2007}\textbf{Scholarship}. Department of Materials Science and Engineering, University of Toronto. \emph{(2 years)}

\years{2006}\textbf{Undergraduate Student Research Award}. National Science and Engineering Research Council of Canada. 

\years{2005}\textbf{Research Summer Studentship Award}. Sunnybrook Health Science Centre.

\years{2004}\textbf{Entrance Scholarship}. Department of Materials Science and Engineering, University of Toronto.
\endgroup

\section*{Publications \& Presentations}

%\subsection*{Invited articles}
%\textbf{Gordon, L.M.}, Joester, D. ``Atom probe tomography of ceramics and biological minerals." \emph{Journal of the American Ceramics Society}, Feature Article. \emph{in preparation}.

%\begingroup\setlength{\parskip}{0.15cm}
%\endgroup

\subsection*{Journal articles}
\textbf{Gordon, L.M.}, Joester, D. “Grain Boundary Chemistry Controls the Properties of Tooth Enamel.” \emph{in preparation}.

\begingroup\setlength{\parskip}{0.15cm}
\textbf{Gordon, L.M.}, Cohen, M.J. Joester, D. “Polymorph Selectivity and Stabilization in Chiton Tooth Ferrihydrite Biomineralization.” \emph{in preparation}.

Suram, S.K., Kaluskar, K., \textbf{Gordon, L.M.}, Joester, D., Rajan, K. “Extracting Crystallographic Information from Atom Probe Tomography of a Biomineral.” \emph{in preparation}.

\years{2013}Marquis, E.A., Bachhav, M., Chen, Y., Dong, Y., \textbf{Gordon, L.M.}, McFacland, A. ``On the current role of atom probe tomography in materials characterization and materials science.'' \emph{Current Opinion in Solid State \& Materials Science}. \emph{in press}.

\years{2012}\textbf{Gordon, L.M.}, Tran, L., Joester, D. “Atom Probe Tomography of Apatites and Bone-Type Mineralized Tissues.” \emph{ACS nano} 6, 10667-10675 (2012). \href{http://dx.doi.org/10.1021/nn3049957}{\textsc{\footnotesize{[doi]}}}

\years{2011}\textbf{Gordon, L.M.}, Joester, D. “Nano-Scale Chemical Tomography of Buried Organic-Inorganic Interfaces in the Chiton Tooth.” \emph{Nature} 469, 194-197 (2011). \href{http://dx.doi.org/10.1038/nature09686}{\textsc{\footnotesize{[doi]}}} Featured in \emph{Nature Methods} 8, 199 (2011). \href{http://dx.doi.org/10.1038/nmeth0311-199}{\textsc{\footnotesize{[doi]}}}

\years{2011}Moss, I., \textbf{Gordon, L.M.}, Woodhouse, K.A., Whyne, C.M., Yee, A.J.M. ``A Novel Thiol-Modified-Hyaluronan and Elastin-Like Polypetide Composite Material for Tissue Engineering of the Nucleus Pulposus of the Intervertebral Disc." \emph{Spine} 36, 1022-1029 (2011). \href{http://dx.doi.org/10.1097/BRS.0b013e3181e7b705}{\textsc{\footnotesize{[doi]}}}

\years{2009}\textbf{Gordon, L.M.}, Bouwhuis, B.A., Suralvo, M., McCrea, J.L., Palumbo, G., Hibbard, G.D. ``Micro-Truss Nanocrystalline Ni Hybrids." \emph{Acta Materialia} 57, 932-939 (2009). \href{http://dx.doi.org/10.1016/j.actamat.2008.10.038}{\textsc{\footnotesize{[doi]}}}

\years{2009}Leung, A., \textbf{Gordon, L.M.}, Skrinskas, T., Szwedowski, T., Whyne, C.M. ``Effects of bone density alterations on strain patterns in the pelvis: application of a finite element model." \emph{Proceedings of the Institution of Mechanical Engineers, Part H: Journal of Engineering in Medicine} 223, 965-979 (2009). \href{http://dx.doi.org/10.1243/09544119JEIM618}{\textsc{\footnotesize{[doi]}}}

\years{2007}Hardisty, M., \textbf{Gordon, L.M.}, Agarwal, P., Skrinskas, T., Whyne, C.M. ``Quantitative characterization of metastatic disease in the spine. Part I. Semiautomated segmentation using atlas-based deformable registration and the level set method." \emph{Medical Physics} 34, 3127 (2007). \href{http://dx.doi.org/10.1118/1.2746498}{\textsc{\footnotesize{[doi]}}}

\years{2007}Whyne, C.M., Hardisty, M., Wu, F., Skrinskas, T., \textbf{Gordon, L.M.}, Clemons, M., Basran, P.S. ``Quantitative characterization of metastatic disease in the spine. Part II. Histogram-based analyses". \emph{Medical Physics} 34, 3279 (2007). \href{http://dx.doi.org/10.1118/1.2756939}{\textsc{\footnotesize{[doi]}}}
\endgroup

\subsection*{Invited Talks}

\years{2013}\textbf{Gordon, L.M.} ``Rock munching mollusks: understanding biomineralization of ultrahard iron-oxide teeth." Harvard University Applied Physics Colloquium. \emph{Cambridge, MA.}

\begingroup\setlength{\parskip}{0.15cm}
\years{2013}\textbf{Gordon, L.M.}, Cohen, M.J., Joester, D. ``New applications: grain boundary and triple junction chemistry in nanocrystalline tooth enamel." Cameca Atom Probe Tomography User Meeting. \emph{Madison, WI.}

\years{2012}\textbf{Gordon, L.M.} ``Defining Interfaces and Interphases." Tomographers Anonymous, Northwestern University. \emph{Evanston, IL.}

\subsection*{Talks}
\years{2013}Cohen, M.J., \textbf{Gordon, L.M.}, Joester, D. ``Correlative Microscopy and Spectroscopy of Buried Interfaces in Tooth Enamel." International Conference on the Chemistry and Biology of Mineralized Tissues. \emph{Lake Geneva, WI.}
\begingroup\setlength{\parskip}{0.15cm}

\years{2013}\textbf{Gordon, L.M.}, Cohen, M.J., Joester, D. ``Grain Boundary Chemistry Controls the Properties of Tooth Enamel." XXII International Materials Research Congress. \emph{Cancun, Mexico.}

\years{2013}\textbf{Gordon, L.M.}, Joester, D. ``Polymorph Selectivity in Chiton Tooth Biomineralization." XXII International Materials Research Congress. \emph{Cancun, Mexico.}

\years{2013}Brooker, L. \textbf{Gordon, L.M.}, Joester, D. ``Characterisation of the microstructure of the aragonite lens of shell eyes in the chiton." XXII International Materials Research Congress. \emph{Cancun, Mexico.}

\years{2013}\textbf{Gordon, L.M.}, Cohen, M.J., Joester, D. ``Correlative Microscopy and Spectroscopy of Buried Interfaces in Tooth Enamel." Microscopy \& Microanalysis Meeting. \emph{Indianapolis, IN.}

\years{2013}\textbf{Gordon, L.M.}, Cohen, M.J., Joester, D. ``Towards Atom Probe Tomography of Hybrid Organic-Inorganic Nanoparticles." Microscopy \& Microanalysis Meeting. \emph{Indianapolis, IN.}

\years{2013}\textbf{Gordon, L.M.}, Cohen, M.J., Joester, D. ``Correlative Microscopy and Spectroscopy of Tooth Enamel." Cameca Atom Probe Tomography User Meeting. \emph{Madison, WI.}

\years{2013}Cohen, M.J., \textbf{Gordon, L.M.}, Suram, S.K., Kaluskar, K., Rajan, K., Valley, J.W., Joester, D. ``Atom Probe Tomography Reconstruction of Single Crystalline Metal Oxides." Cameca Atom Probe Tomography User Meeting. \emph{Madison, WI.}

\years{2013}\textbf{Gordon, L.M.}, ``Nanoscale Chemical Tomography of Buried Organic-Inorganic Interfaces" McMaster University, Materials Science and Engineering Department Seminar. \emph{Hamilton, ON.}

\years{2013}\textbf{Gordon, L.M.}, Joester, D. ``Understanding the biological stabilization of ferrihydrite and its transformation to magnetite." American Physical Society Meeting. \emph{Baltimore, MD.}

\years{2012}\textbf{Gordon, L.M.}, Joester, D. ``Buried Interfaces in Mouse Incisor Enamel." Spring Meeting of the Materials Research Society. \emph{San Francisco, CA.}

\years{2011}\textbf{Gordon, L.M.}, Joester, D. ``Atom Probe Tomography of Buried Organic-Inorganic Interfaces in Biological Minerals." Society of Engineering Science Meeting. \emph{Evanston, IL.}

\years{2011}\textbf{Gordon, L.M.}, Joester, D. ``Buried Organic-Inorganic Interfaces in Mineralized Biological Tissues." 11\textsuperscript{th} International Symposium on Biomineralization. \emph{Noosa, Queensland, Australia.}

\years{2011}\textbf{Gordon, L.M.}, Joester, D. ``Buried Organic-Inorganic Interfaces in Biological Minerals." Cameca Atom Probe Tomography User Meeting. \emph{Madison, WI.}

\years{2009}\textbf{Gordon, L.M.}, Joester, D. ``Atom Probe Tomgraphy of Buried Organic in the Chiton Tooth." Fall Meeting of the Materials Research Society. \emph{Boston, MA.}

\years{2006}\textbf{Gordon, L.M.}, Hardisty, M., Skrinskas, T., Wu, F., Whyne, C.M. ``Automated Atlas-based 3D segmentation of the Metastatic Spine." 40\textsuperscript{th} Annual Canadian Orthopaedic Research Society Meeting. \emph{Toronto, ON.}
\endgroup

\subsection*{Published Proceedings}
\years{2013}\textbf{Gordon, L.M.}, Cohen, M.J., Joester, D. ``Towards Atom Probe Tomography of Hybrid Organic-Inorganic Nanoparticles." \emph{Microscopy \& Microanalysis}. 19, Supplement S2, 952-953 (2013)
\begingroup\setlength{\parskip}{0.15cm}

\years{2013}\textbf{Gordon, L.M.}, Cohen, M.J., Joester, D. ``Correlative Microscopy and Spectroscopy of Buried Interfaces in Tooth Enamel." \emph{Microscopy \& Microanalysis}. 19, Supplement S2, 1634-1635 (2013)

\years{2013}Larson, D.J., Valley, J.W., Ushikubo, T., Miller, M.K., Takamizawa, H., Shimizu, Y., \textbf{Gordon, L.M.}, Joester, D. Giddings, D., Reinhard, D.A., Prosa, T.J., Olson, D.P., Lawrence, D.F., Clifton, P.H., Ulfig, R.M., Martin, I., Kelly, T.F. ``New Applications in Atom Probe Tomography." \emph{Microscopy \& Microanalysis}. 19, Supplement S2, 1022-1023 (2013)

\years{2013}Cohen, M.J., \textbf{Gordon, L.M.}, Suram, S., Kaluskar, K., Rajan, K., Valley, J.W., Joester, D. ``Constraining Atom Probe Tomography Reconstructions of Crystalline Oxides." \emph{Microscopy \& Microanalysis}. 19, Supplement S2, 1010-1011 (2013)

\years{2013}\textbf{Gordon, L.M.}, Joester, D. ``Understanding the biological stabilization of ferrihydrite and its transformation to magnetite" \emph{Bulletin of the American Physical Society}. (2013)

\years{2012}Suram, S.K., Kaluskar, K., \textbf{Gordon, L.M.}, Joester, D., Rajan, K. ``Atom Probe Tomography of Organic/Inorganic Interfaces in Biominerals." \emph{Microscopy \& Microanalysis}. 18, Supplement S2, 1608-1609 (2012)

\years{2012}Larson, D.J., Smentkowski, V.S., \textbf{Gordon, L.M.}, Joester, D., Inoue, K.,  Reinhard, D.A., Prosa, T.J., Olson, D., Lawrence, D., Clifton, P.H., Ulfig, R.M., Martin, I., Snoeyenbos, D., Kelly, T.F. ``New Applications in Atom Probe Tomography." \emph{Microscopy \& Microanalysis}. 18, Supplement S2, 926-927 (2012)

\years{2008}\textbf{Gordon, L.M.}, Hardisty, M., Skrinskas, T., Wu, F., Whyne, C.M. ``Automated Atlas-based 3D segmentation of the Metastatic Spine." \emph{Journal of Bone and Joint Surgery, British Volume} 90 Supplement 1, 128 (2008)

\years{2008}Wu, F., Burnes, D., \textbf{Gordon, L.M.}, Hardisty, M., Skrinskas, T., Basran, P., Whyne, C.M. ``Quantitative Characterization of Metastatic Disease in the Spine and Development of and Automated Tracking Tool."  \emph{Journal of Bone and Joint Surgery, British Volume} 90 Supplement 1, 129 (2008)

\years{2008}Whyne, C.N,, Skrinskas, T., Yee, A., \textbf{Gordon, L.M.}, Akens, M., Hardisty, M., Burch, S., Wilson, B., Bisland, S., ``Does Photodynamic Therapy Affect the Structural Integrity of Vertebral Bone." \emph{Journal of Bone and Joint Surgery, British Volume} 90 Supplement 1, 135 (2008)

\subsection*{Posters}
\years{2013}Larson, D., Ulfig, R., Valley, J., Ushikubo, T., Miller, M., Takamizawa, H., Shimizu, Y., \textbf{Gordon, L.M.}, Joester, D., Duquenne, C., Giddings, A., Reinhard, D., Lawrence, D., Clifton, P. ``New Applications in Atom Probe Tomography" Microscopy \& Microanalysis Meeting. \emph{Indianapolis, IN.}

\years{2013}Cohen, M.J., \textbf{Gordon, L.M.}, Suram, S.K., Kaluskar, K., Rajan, K., Valley, J.W., Joester, D. ``Constraining Atom Probe Tomography Reconstructions of Crystalline Oxides." Microscopy \& Microanalysis Meeting. \emph{Indianapolis, IN.}

\years{2013}Ulfig, R., Valley, J., Ushikubo, T., Miller, M., Takamizawa, H., Shimizu, Y., \textbf{Gordon, L.M.}, Joester, D., Duquenne, C., Giddings, A., Reinhard, D., Lawrence, D., Clifton, P., Larson, D. ``New Applications of LEAP® Microscopy" 15th European Conference on Applications of Surface and Interface Analysis. \emph{Forte Village Resort, Sardinia, Italy}.

\years{2013}\textbf{Gordon, L.M.}, Joester, D. ``Buried Organic/Inorganic Interfaces in Biological Minerals" Northwestern University John E. Hilliard Memorial Symposium. \emph{Evanston, IL.}

\years{2012}Ehrke, H.U., Smentkowski, V.S., \textbf{Gordon, L.M.}, Joester, D., Prosa, T.J., Clifton, P.H., Snoeyenbos, D., ``Atom Probe Tomography - 3D Subnanometer chemical imaging extended to Photovoltaic and Geological Materials." European Mineralogical Conference . \emph{Frankfurt, Germany.}

\years{2012}Ehrke, H.U., Larson, D.J., Smentkowski, V.S., \textbf{Gordon, L.M.}, Joester, D., Prosa, T.J., Clifton, P.H., Snoeyenbos, D., ``New Applications in Atom Probe Tomography." Microscopy \& Microanalysis. \emph{Phoenix, AZ.}

\years{2012}\textbf{Gordon, L.M.}, Joester, D. ``Model System for Biomimetic Magnetite Mineralization" Gordon Research Conference on Biomineralization. \emph{New London, NH.}

\years{2012}Larson, D.J., Smentkowski, V.S., \textbf{Gordon, L.M.}, Joester, D., Inoue, K.,  Reinhard, D.A., Prosa, T.J., Olson, D., Lawrence, D., Clifton, P.H., Ulfig, R.M., Martin, I., Snoeyenbos, D., Kelly, T.F. ``New Applications in Atom Probe Tomography." Microscopy \& Microanalysis. \emph{Phoenix, AZ.}

\years{2012}Suram, S.K., Kaluskar, K., \textbf{Gordon, L.M.}, Joester, D., Rajan, K. ``Atom Probe Tomography of Organic/Inorganic Interfaces in Biominerals." Microscopy \& Microanalysis. \emph{Phoenix, AZ.}

\years{2012}Larson, D.J., Smentkowski, V.S., \textbf{Gordon, L.M.}, Joester, D., Inoue, K.,  Reinhard, D.A., Prosa, T.J., Olson, D., Lawrence, D., Clifton, P.H., Ulfig, R.M., Martin, I., Snoeyenbos, D., Horreard, F., Kelly, T.F. ``New Applications in Atom Probe Tomography." SCANDEM 2012: Annual Meeting of the Nordic Microscopy Society. \emph{Bergen, Norway}

\years{2012}Larson, D.J., Smentkowski, V.S., \textbf{Gordon, L.M.}, Joester, D., Inoue, K.,  Reinhard, D.A., Prosa, T.J., Olson, D., Lawrence, D., Clifton, P.H., Ulfig, R.M., Martin, I., Snoeyenbos, D.,  Kelly, T.F. ``New Applications in Atom Probe Tomography." International Field Emission Symposium. \emph{Tuscaloosa, AL.}

\years{2010}\textbf{Gordon, L.M.}, Joester, D. ``Nanoscale Chemical Tomography of Buried Organic-Inorganic Interfaces in Biominerals." Gordon Research Conference on Biomineralization. \emph{New London, NH.}

\years{2006}Hardisty, M., Skrinskas, T., \textbf{Gordon, L.M.}, Whyne, C.M. ``A Repeatable Bone Quality Measurement Techniquiqe Using 3D Stereology." 40\textsuperscript{th} Annual Canadian Orthopaedic Research Society Meeting. \emph{Toronto, ON.}

\years{2006}Whyne, C.M., Skrinskas, T., Yee, A., \textbf{Gordon, L.M.}, Akens, M., Hardisty, M., Burch, S., Wilson, B., Bisland, S. ``Does Photodynamic Therapy Affect the Structural Integrity of Vertebral Bone?" 40\textsuperscript{th} Annual Canadian Orthopaedic Research Society  Meeting. \emph{Toronto, ON.}

\years{2006}Wu, F., Burnes, D., \textbf{Gordon, L.M.}, Hardisty, M., Skrinskas, T., Basran, P., Whyne, C.M. ``Quantitative Characterization of Metastatic Disease in the Spine and Development of an Automated Tracking Tool." 40\textsuperscript{th} Annual Canadian Orthopaedic Research Society Meeting. \emph{Toronto, ON.}

\years{2006}\textbf{Gordon, L.M.}, Hardisty, M., Skrinskas, T., Wu, F., Whyne, C.M. ``Atlas-Based Segmentation in the Metastatic Spine via 3D Deformable Registration." 52\textsuperscript{nd} Annual Meeting of the Orthopaedic Research Society. \emph{Chicago, IL.}

\years{2006}Hardisty, M., Skrinskas, T., \textbf{Gordon, L.M.}, Whyne, C.M. ``A Repeatable Stereologic Method to Measure Bone Quality." 52\textsuperscript{nd} Annual Meeting of the Orthopaedic Research Society. \emph{Chicago, IL.}

\years{2006}Whyne, C.N,, Skrinskas, T., Yee, A., \textbf{Gordon, L.M.}, Akens, M., Hardisty, M., Burch, S., Wilson, B., Bisland, S., ``Structural Effects of Photodynamic Therapy on Vertebral Bone. 52\textsuperscript{nd} Annual Meeting of the Orthopaedic Research Society." \emph{Chicago, IL.}

\years{2006}Wu, F., Burnes, D., \textbf{Gordon, L.M.}, Hardisty, M., Skrinskas, T., Basran, P., Whyne, C.M. ``Quantitative Characterization of Metastatic Disease in the Spine and Development of and Automated Tracking Tool." 52\textsuperscript{nd} Annual Meeting of the Orthopaedic Research Society. \emph{Chicago, IL.}
\endgroup

\section*{Media Coverage}
%\years{2013}``Zoologger: mollusc grows hardest teeth in the world", Ziya Tong and Dan Riskin, \emph{Daily Planet: Discovery Channel Canada}. October 2013. \href{http://www.newscientist.com/article/dn24329-zoologger-mollusc-grows-hardest-teeth-in-the-world.html#.Uk7GpMakpHV}{\textsc{\footnotesize{[url]}}}

\years{2013}``Zoologger: mollusc grows hardest teeth in the world", Alyssa Botelho, \emph{New Scientist}. October 2013. \href{http://www.newscientist.com/article/dn24329-zoologger-mollusc-grows-hardest-teeth-in-the-world.html#.Uk7GpMakpHV}{\textsc{\footnotesize{[url]}}} Featured on \emph{Newscientist.com} front page \href{http://lylegordon.ca/newsci.jpg}{\textsc{\footnotesize{[cache]}}}
\begingroup\setlength{\parskip}{0.1cm}

\years{2013}``Tough Teeth Inspire New Bio-designs", Susan Reiss, \emph{Research.gov}. June 5\textsuperscript{th}, 2013. \href{http://www.research.gov/research-portal/appmanager/base/desktop;jsessionid=hFFMRyhFTMl4CQ76t1456YQ7LXd1RJYjQGVG1gmHP2Jcsny3ryW0!2110096251!130307470?_nfpb=true&_windowLabel=assetsInTheStates_1&_urlType=action&assetsInTheStates_1_action=selectAwardDetail&assetsInTheStates_1_id=%2FresearchGov/AwardHighlight/PublicAffairs/23492_ToughTeethInspireNewBio-designs.html}{\textsc{\footnotesize{[url]}}} 

\years{2013}``Strange Biology Inspires the Best New Materials", Nadia Drake, \emph{Wired}. Mar 27\textsuperscript{th}, 2013. \href{http://www.wired.com/wiredscience/2013/03/biomimetic-materials/?utm_source=feedburner&utm_medium=feed&utm_campaign=Feed%3A+wired%2Findex+%28Wired%3A+Top+Stories%29&pid=6577}{\textsc{\footnotesize{[url]}}}\\ Featured on \emph{Wired.com} front page \href{http://lylegordon.ca/wired.jpg}{\textsc{\footnotesize{[cache]}}}

\years{2011}``Rock-Munching Mollusks A Model For Artificial Bones", Joe Palca, \emph{National Public Radio}. January 13\textsuperscript{th}, 2011. \href{http://www.npr.org/2011/01/13/132859853/rock-munching-mollusks-a-model-for-artificial-bones}{\textsc{\footnotesize{[url]}}} \href{http://lylegordon.ca/audio/npr-2011-01-13.mp3}{\textsc{\footnotesize{[mp3]}}}  \href{http://lylegordon.ca/nprtranscript.html}{\textsc{\footnotesize{[transcript]}}}

\years{2011}``Teething trouble", Kerri Smith et al., \emph{Nature podcast}. Jan 13\textsuperscript{th}, 2011. \href{http://www.nature.com/nature/podcast/index-2011-01-13.html}{\textsc{\footnotesize{[url]}}} \href{http://lylegordon.ca/audio/nature-2011-01-13.mp3}{\textsc{\footnotesize{[mp3]}}}

\years{2011}``Imaging organic-inorganic interfaces in the tooth", \emph{Nature Methods} 8, 199 (2011). \href{http://dx.doi.org/10.1038/nmeth0311-199}{\textsc{\footnotesize{[doi]}}}

\years{2011} ``Cracking a Tooth". \emph{US News}. Jan 13\textsuperscript{th}, 2011. \href{http://www.usnews.com/science/articles/2011/01/13/cracking-a-tooth}{\textsc{\footnotesize{[url]}}}
\endgroup

\section*{Awards}
\years{2013}\textbf{Microscopy \& Microanalysis Presidential Scholar Award}, Microscopy Society of America and the Microanalysis Society.

\begingroup\setlength{\parskip}{0.1cm}
\years{2009}\textbf{Finalist}. Materials Research Society Science as Art Competition.

\years{2009}\textbf{Image of Distinction}. Nikon Small World --- Photomicrography Competition. \href{http://www.nikonsmallworld.com/detail/year/2009/66}{\textsc{\footnotesize{[url]}}} \href{http://lylegordon.ca/nikon2009.jpg}{\textsc{\footnotesize{[image]}}}

\years{2008}\textbf{First Place: Technical Report.} Canadian National Concrete Canoe Competition, Halifax, NS.

\years{2007}\textbf{First Place: Technical Presentation.} Canadian National Concrete Canoe Competition, Kingston, ON.
\endgroup

\section*{Professional Service \& Extracurriculars}
\years{2013}Symposium Assistant, XXII International Materials Research Congress (IMRC). Cancun, Mexico.

\years{2013}Session Chair, Cameca Atom Probe Tomography User Meeting. Madison, WI.

\years{2012}Symposium Assistant, Materials Research Society Spring Meeting. San Francisco, CA.

\begingroup\setlength{\parskip}{0.1cm}
\years{2010}Science Fair Judge. Chicago Public Schools, Area 9.

\years{2010}Science Fair Judge. Chicago Public Schools, Area 4.

\years{2009}Student-Faculty Representative, Materials Science Student Association, Northwestern University.

\years{2007-2008}Project manager, University of Toronto Concrete Canoe Team.

\years{2007}Tutored high-school level physics and math.

\years{2006-2008}Mentored first year Materials Science and Engineering students, University of Toronto.

\years{2005-2007}Head of concrete mix and composite design, University of Toronto Concrete Canoe Team.

\years{2006}Vice-chair coordinating orientation week and distributing financial aid for one thousand incoming University of Toronto engineering students.

\years{2003}Solo Photography Exhibition, Albert White Gallery. Toronto, ON.
\endgroup

\section*{Professional Societies}
American Association for the Advancement of Science, American Physical Society, Materials Research Society, Microanalysis Society, Microscopy Society of America.